Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-11-27 Moltres.tex
Describe peak power density.

Molten salt reactor concepts garnered considerable interest in the 1950s and 60s
with development of the \gls{ARE} and later the \gls{MSRE} at \gls{ORNL}.  With
the inclusion of the \gls{MSR} among the Generation-IV reactor designs
\cite{gif_generation_2008,gif_generation_2015}, this reactor concept has gained renewed research
interest in the past decade, with many new nuclear companies proposing both
fluid-fuelled and solid-fuelled commercial \gls{MSR} designs
\cite{hyde_liquid_2015,leblanc_integral_2015,thorcon_-able_2017,scarlat_design_2014,transatomic_power_corporation_neutronics_2016}. 
The key advantages of \gls{MSR}s generally pertain to improved fuel utilization
and reactor safety. In contrast to legacy reactors, only moderator fast neutron
damage and fuel chemistry evolution limit burnup. A clever configuration of moderator
as in \cite{engel_conceptual_1980} can enable reactor operation without opening the vessel
for thirty or more years. Further, several fission products selectively precipitate onto
nickel surfaces in fluoride salt, as documented in \cite{engel_conceptual_1980}, thus reducing
unwanted neutron absorption. Lastly, the epithermal spectrum of graphite-moderated salt reactors
incinerates plutonium more efficiently, thus reducing long-lived transuranic waste production \cite{engel_conceptual_1980}. 
The sum of the aforementioned benefits imply spent nuclear fuel
mass can be reduced in comparison to legacy reactors.
Due to these characteristics, the \gls{MSR} is potentially uniquely capable of 
extending fuel resources and ameliorating spent fuel burden.

>>>>

Molten salt reactor concepts garnered considerable interest in the 1950s and 60s
with development of the \gls{ARE} and later the \gls{MSRE} at \gls{ORNL}.  With
the inclusion of the \gls{MSR} among the Generation-IV reactor designs
\cite{gif_generation_2008,gif_generation_2015}, this reactor concept has gained renewed research
interest in the past decade, with many new nuclear companies proposing both
fluid-fuelled and solid-fuelled commercial \gls{MSR} designs
\cite{hyde_liquid_2015,leblanc_integral_2015,thorcon_-able_2017,scarlat_design_2014,transatomic_power_corporation_neutronics_2016}. 
The key advantages of \gls{MSR}s generally pertain to improved fuel utilization
and reactor safety. In contrast to legacy reactors, only moderator fast neutron
damage and fuel chemistry evolution limit burnup. A clever configuration of moderator
as in \cite{engel_conceptual_1980} can enable reactor operation without opening the vessel
for thirty or more years. Further, several fission products selectively precipitate onto
nickel surfaces in fluoride salt, as documented in \cite{engel_conceptual_1980}, thus reducing
unwanted neutron absorption. Lastly, the epithermal spectrum of graphite-moderated salt reactors
incinerates plutonium more efficiently, thus reducing long-lived transuranic waste production \cite{engel_conceptual_1980}. 
The sum of these characteristics implies the \gls{MSR} uniqely ameliorates spent fuel burden whilst
extending nuclear fuel resources. To top all these benefits off, xenon transients become moot in
\gls{MSR}s due to its insolubility in salt, thus narrowing transient analysis focus to thermalhydraulic
concerns.
